Fractional Types

### 2013-02-25 frac.tex
small clarification of piTF modelled by sets and relations

\noindent 
Types include the unit type {{1}}, sum types {{b1+b2}}, and
product types {{b1*b2}}.  Values includes {{()}} which is the only value of
type {{1}}, {{left v}} and {{right v}} which inject~{{v}} into a sum type,
and {{(v1,v2)}} which builds a value of product type. 
%% But these values should be regarded as largely ancillary: we do not
%% treat them as first-class citizens, and they only occur when observing
%% the effect of an isomorphism.

@@

\vspace{-10pt}
\noindent From a programming perspective, we think of a value {{1/v}} as a
\emph{first-class constraint} that can only be satisfied if it is matched
with an actual value {{v}} or as a \emph{pattern} representing the absence of
some information of a specific shape (i.e., \emph{negative information}),
that can only be reconciliated by an actual value {{v}}. The combinator
{{eta*_b : 1 <-> 1/b * b}} thus represents a fission point which creates ---
out of no information --- an equal amount of negative and positive
information. Symmetrically, the combinator {{eps*_b : 1/b * b <-> 1}} matches
up an equal amount of negative and positive information producing no residual
information.

@@

In this section, we provide a simple semantics of {{PiTF}} in the category of
finite sets and relations. We interpret each combinator {{c : b1 <-> b2}} as
a \emph{relation} between the sets denoted by {{b1}} and {{b2}}
respectively. As we illustrate, this semantics allows \emph{arbitrary}
relations (including the empty relation and relations that are not
isomorphisms) to be represented as values in {{PiTF}}.  In Sec.~\ref{sec:cat}
we discuss more refined semantics that are more suitable for richer
categories.

>>>>

\noindent 
Types include the unit type {{1}}, sum types {{b1+b2}}, and
products types {{b1*b2}}.  Values includes {{()}} which is the only value of
type {{1}}, {{left v}} and {{right v}} which inject~{{v}} into a sum type,
and {{(v1,v2)}} which builds a value of product type. 
%% But these values should be regarded as largely ancillary: we do not
%% treat them as first-class citizens, and they only occur when observing
%% the effect of an isomorphism.

@@

\vspace{-10pt}
\noindent From a programming perspective, we think of a value {{1/v}} as a
\emph{first-class constraint} that can only be satisfied if it is matched
with an actual value {{v}}. In other words, {{1/v}} is a \emph{pattern} representing the absence of
some information of a specific shape (i.e., \emph{negative information}),
that can only be reconciliated by an actual value {{v}}. The combinator
{{eta*_b : 1 <-> 1/b * b}} thus represents a fission point which creates ---
out of no information --- an equal amount of negative and positive
information. Symmetrically, the combinator {{eps*_b : 1/b * b <-> 1}} matches
up an equal amount of negative and positive information producing no residual
information.

@@

In this section, we provide a simple semantics of {{PiTF}} in the
category of finite sets and relations, in the following way: We
interpret each combinator {{c : b1 <-> b2}} as a \emph{relation}
between the sets denoted by {{b1}} and {{b2}} respectively. Sets
{{b1}} and {{b2}} can be related only if the same information measure.
As we illustrate, this semantics allows \emph{arbitrary} relations
(including the empty relation and relations that are not isomorphisms)
to be represented as values in {{PiTF}}.  In Sec.~\ref{sec:cat} we
discuss more refined semantics that are more suitable for richer
categories.
